%-------------------------
% Resume in Latex
% Author : Vanshaj Saxena
% Website: https://github.com/vanshajsaxena/resume
% License : MIT
%------------------------

\documentclass[a4paper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
%\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{5pt} % Set a minimum foot skip to satisfy fancyhdr
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in} % reclaim the text area reduced by `\oddsidemargin`
\addtolength{\topmargin}{-.5in} % need .5in space from top
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

% Ensure that generate pdf is machine readable/ATS parsable
%\pdfgentounicode=1 % no need with tectonic

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%


\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.vanshajsaxena.com/}{\Huge Vanshaj Saxena}} & \raisebox{-0.5ex}{\faEnvelope[regular]} \underline{\href{mailto:contact@vanshajsaxena.com}{contact@vanshajsaxena.com}}\\
  \raisebox{-0.5ex}{\faGlobe} \underline{\href{https://www.vanshajsaxena.com/}{vanshajsaxena.com}} \quad
  \raisebox{-0.5ex}{\faGithub} \underline{\href{https://www.github.com/vanshajsaxena}{vanshajsaxena}}
 & Mobile : +91-76685-66620 \\
\end{tabular*}

% \begin{center}
%     \textbf{\Huge \scshape Vanshaj Saxena} \\ \vspace{1pt}
%     \small +91-76685-66620 $|$ \href{mailto:vanshajsaxena2005@gmail.com}{\underline{vanshajsaxena2005@gmail.com}} $|$
%     \href{https://linkedin.com/in/vanshajsaxenaxyz}{\underline{linkedin.com/in/vanshajsaxenaxyz}} $|$
%     \href{https://github.com/VanshajSaxena}{\underline{github.com/vanshajsaxena}}
% \end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Galgotias University}{Aug. 2021 -- Aug. 2025}
      {Bachelor of Technology in Computer Science Engineering (8.5/10)} {Greater Noida, UP}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Developer Trainee}{July 2025 - Present}
      {United Registrar of Systems}{Noida, UP}
      \resumeItemListStart
        \resumeItem{Maintained and enhanced internal tools and backend systems supporting nationwide operations, improving system reliability, scalability, and performance to ensure consistent availability under operational load.}
        \resumeItem{Modernized a business-critical module of a 15-year-old Web Forms application by re-architecting it with React and TypeScript, reducing technical debt and improving maintainability, performance, and long-term scalability.}
        \resumeItem{Engineered a backend API for programmatic MS Word document generation and manipulation, automating routine reporting workflows and reducing manual report preparation time by approximately 50\% for business operations.}
      \resumeItemListEnd
    \resumeSubheading
      {Founder \& Engineer}{Dec. 2025 - Present}
      {Printit $|$ https://printit.ink/}{Ghaziabad, UP}
      \resumeItemListStart
        \resumeItem{Built a SaaS product from scratch as a solo founder, owning the product journey from idea, design, and development through to launch.}
        \resumeItem{Replaced a manual, high-friction printing workflow with a streamlined self-serve experience, reducing operational overhead, minimizing user effort, and improving overall workflow efficiency and user experience.}
        \resumeItem{Enabled users to initiate print jobs in a simple three-step process from anywhere via a QR scan, significantly increasing accessibility and reducing turnaround time.}
      \resumeItemListEnd
    \resumeSubheading
      {iOS Intern}{June 2024 - July 2024}
      {Infosys Limited}{Mysuru, KA}
      \resumeItemListStart
        \resumeItem{Contributed to the development of a SaaS-based Library Management System (LMS), focusing on testing integrations and building and delivering key product features.}
        \resumeItem{Served as Scrum Master for a 10-member Agile team, facilitating sprint planning, execution, and delivery to ensure smooth and timely releases.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% -----------Multiple Positions Heading-----
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
% ------------------------------------------

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{\underline{\href{https://printit.ink}{Printit}}} $|$ \emph{TypeScript, C\#, React, Electron, NestJS, PostgreSQL, WebSockets}}{Dec. 2025 - Present}
        \resumeItemListStart
          \resumeItem{Architected and deployed a multi-tenant SaaS platform integrating a Progressive Web App, an Electron-based desktop client, and a containerized NestJS backend, with tenant isolation, scalable service orchestration, and a unified API layer supporting cross-platform clients.}
          \resumeItem{Engineered the Desktop Application and PWA to automate manual printing workflows using an asynchronous, event-driven architecture, enabling non-blocking job orchestration and real-time status propagation of print job lifecycle events.}
          \resumeItem{Designed and implemented a thin abstraction layer over the Windows Print Spooler API, normalizing device-specific behaviors and handling driver inconsistencies to provide a consistent, fault-tolerant printing interface.}
          \resumeItem{Implemented a PWA-driven job submission model that abstracts print workflows into a minimal three-step state machine, leveraging offline-capable service workers, enabling device-agnostic job initiation with real-time state propagation.}
        \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{{URS Backend}} $|$ \emph{TypeScript, C\#, React, ASP.NET Core, Zustand, Tanstack, IDB}}{July 2025 - Present}
        \resumeItemListStart
          \resumeItem{Refactored a legacy Web Forms module by decoupling business logic from the presentation layer, introducing a clear client-server separation that improved maintainability, testability, and scalability of the application architecture.}
          \resumeItem{Developed a backend API for generation of OpenXML-compliant Word documents, implementing a template-driven engine that parses and replaces tagged placeholders with database-backed data to produce structured, automated business reports.}
          \resumeItem{Developed a single-page application (SPA) using React and TypeScript, optimized with Vite (Rollup) for fast builds and HMR, leveraging Zustand for lightweight client-side state management and TanStack Query for efficient server-state synchronization, caching, and data fetching.}
        \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{\underline{\href{https://github.com/VanshajSaxena/auction-system}{Auction Hub}}} $|$ \emph{Java, Spring Boot, Hibernate, OpenAPI, JUnit, REST, JPA}}{Dec. 2024 - Mar. 2025}
        \resumeItemListStart
          \resumeItem{Designed and developed a Spring Boot 3 application for online auctions, exposing RESTful endpoints for user management, product listing, bidding, and auction scheduling.}
          \resumeItem{Created a secure platform with the use of Spring Security and JWT based authorization, enforcing role-based access control and stateless authentication.}
        \resumeItemListEnd
    \resumeProjectHeading
    {\textbf{\underline{\href{https://github.com/VanshajSaxena/LMS_User}{Fable}}} $|$ \emph{Swift, SwiftUI, Firebase/Firestore, Git}}{June 2024 - July 2024}
        \resumeItemListStart
          \resumeItem{Contributed to the development of a multi-tenant SaaS application using SwiftUI, integrating Firebase Authentication and Cloud Firestore to implement secure user authentication, tenant-aware access control, and real-time data synchronization.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}{: TypeScript, C\#, Java} \\
    \textbf{Databases}{: MS SQL, PostgreSQL, Firestore} \\
    \textbf{Frameworks \& Tools}{: React, ASP.NET Core, Zustand, Tanstack, Spring Boot, Git, Unix/Linux} \\
    \textbf{Concepts}{: Object Oriented Programming, Functional Programming, Concurrency, REST, Software Development, Networking Fundamentals, Performance Tuning, Security Fundamentals, Source Control}
    }}
  \end{itemize}
\end{document}
